### 2021-08-02 paper/paper.tex
added funding and resources for ARW to acknowledgements

We would like to thank all other contributors to and users of \trixi for their
help, encouragement, and discussions.
Funded by the Deutsche Forschungsgemeinschaft (DFG, German Research Foundation)
under Germany's Excellence Strategy EXC 2044-390685587, Mathematics Münster:
Dynamics-Geometry-Structure.

>>>>

We would like to thank all other contributors to and users of \trixi for their
help, encouragement, and discussions.
Funded by the Deutsche Forschungsgemeinschaft (DFG, German Research Foundation)
under Germany's Excellence Strategy EXC 2044-390685587, Mathematics Münster:
Dynamics-Geometry-Structure.
Andrew Winters was funded through Vetenskapsr{\aa}det, Sweden grant
agreement 2020-03642 VR.

The performance computations were enabled by resources provided by the Swedish National
Infrastructure for Computing (SNIC) at Tetralith partially funded by the Swedish
Research Council through grant agreement no. 2018-05973.
